---
title: "Homework 1"
author: Danyang Gui
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```


Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not charactor or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


Convert the logical vector and then multiply the random sample by the result


```{r try_convert and multiply}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


##Problem 2


`r data("penguins", package = "palmerpenguins")`

`r names(penguins) `
Variables include "species", "island", "bill_length_mm", "bill_depth_mm", flipper_length_mm", "body_mass_g", "sex", and "year"             

`r summary(penguins)`

`r nrow(penguins)`
`r ncol(penguins)`
This data set has 344 rows and 8 columns, which means that this penguins data set has 344 observations of 8 variables.


`r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`
The mean flipper length calculated from existing values equals 200.92mm

`r scatterplot <- ggplot(penguins, aes (x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()`


