---
title: "Homework 1"
author: Danyang Gui
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements. 

```{r create_df}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```


Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not charactor or factor. 

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


Convert the logical vector and then multiply the random sample by the result


```{r try_convert and multiply}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```


##Problem 2


`r data("penguins", package = "palmerpenguins")`

This penguins dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns, which means that it has `r nrow(penguins)` observations of `r ncol(penguins)` variables.

Variables include `r names(penguins)`.     

Out of the 344 penguins, `r length (filter(penguins, species == "Adelie") %>% pull(species))` of the penguins belong to the species of Adelie. `r length (filter(penguins, species == "Chinstrap") %>% pull(species))` are Chinstrap and `r length (filter(penguins, species == "Gentoo") %>% pull(species))` are Gentoo.

The smallest bill length is `r min(pull(penguins, bill_length_mm), na.rm=TRUE) `mm.
The largest bill depth is `r max(pull(penguins, bill_length_mm), na.rm=TRUE) `mm.
The median of body mass equals `r mean(pull(penguins, body_mass_g), na.rm=TRUE)`g.
The mean flipper length calculated from existing values equals `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`mm.




A scatterplot of flipper_length_mm (y) vs bill_length_mm (x) is generated using the code below: 
 
```{r}
ggplot(penguins, aes (x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatterplot.pdf",  width = 3.5, height = 3.5)
```

Export my first scatterplot to my project directory as a pdf file using ggsave.
